---
title: "Alcohol vs Seat choice"
author: "Erika Mondragon"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

$H_0$: There is no difference in the alcohol consumed based the row you sit in

$H_A$: There is a difference in the alcohol consumed based the row you sit in

# Methods

The response variable is numerical and the the explanatory variable is categorical. Alcohol  is a numerical, seat is numerical. We will use the numerical~cat file. 

## Results 

### Graphical Results 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The graph shows the amount of alcohol consumed. In the backseats they drink the most, middle seats and front seats drink the around the same amount. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot show the amount of alcohol based on where you sit. Those who sit in the back seats consume the most alcohol. While those in the middle seat drink around the same amount as those in the front seats. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

This data shows the mean and median of the alcohol consumed in the back, middle and front seats. Those who sit in the back seats drink at least three times than those who sit in the middle and front seats. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116, which is lower than 0.5. Therefore, we reject the null hypothesis. This means that there is a difference in the alcohol consumed based on the row a person sits in. 

```{r}
plot(TukeyHSD(model1))
```

We don't have the evidence that there is a difference in the alcohol consumption between the middle and front rows. The only difference found is that the back rows consumes more alcohol than the front and middle rows. 

## Conclusions

The original question was, is there a difference between the alcohol consumed between the row you choose to sit in? Yes, there is a difference between the alcohol consumed based on where a person sits in. Since the p-value is 0.000116, which is lower than 0.5, we reject the null hypothesis. Based on the evidence, we conclude that there is a difference in the alcohol consumed based on the row a person sits in. 

