---
title: "Alcohol vs Seat choice"
author: "Erika Mondragon"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

$H_0$: There is no difference in the alcohol consumed based the row you sit in

$H_A$: There is a difference in the alcohol consumed based the row you sit in

# Methods

The response variable is numerical and the the explanatory variable is categorical. Alcohol  is a numerical, seat is numerical. We will use the numerical cat file. 

## Results 

### Graphical Results 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The graph shows the amount of alcohol consumed. In the backseats they drink the most, middle seats and front seats drink the around the same amount. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot show the amount of alcohol based on where you sit. Those who sit in the back seats consume the most alcohol. While those in the middle seat drink a little more than those in the front seats. 

## Numerical Summarys 

## Inferential Tests

## Conclusions


